A/Bテストの分析

### 2024-08-28 posts/ABIDE/analysis.qmd
2nd trial in rendering.

---
title: "A/Bテストの分析"
author: "Seiro Ito"
execute: 
  echo: false
format:
  html:
    toc: true
    toc-location: left
    number-sections: true
    number-depth: 2
    embed-resources: true
    smooth-scroll: true
    anchor-sections: true
bibliography: ../seiro.bib
resources:
  - analysis.pdf
# setwd("C:/seiro/docs/personal/Miscelleneous/QuartoFiles/posts/ABIDE/"); quarto::quarto_render("analysis.qmd")
# quarto render analysis.qmd
---
<style>
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>

>>>>

---
title: "A/Bテストの分析"
author: "Seiro Ito"
execute: 
  echo: false
  freeze: auto
format:
  html:
    toc: true
    toc-location: left
    number-sections: true
    number-depth: 2
    embed-resources: true
    smooth-scroll: true
    anchor-sections: true
bibliography: ../seiro.bib
resources:
  - analysis.pdf
# setwd("C:/seiro/docs/personal/Miscelleneous/QuartoFiles/posts/ABIDE/"); quarto::quarto_render("analysis.qmd")
# quarto render analysis.qmd
---
<style>
br {
  /* change <br> space length*/
  display: block; /* makes it have a width */
  content: ""; /* clears default height */
  margin-top: 10px; /* change this to whatever height you want it */
}
</style>
